---
title: "R Packages for LASSO"
author: "Zhou Ya"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Generate Data

## Get normalized data "XData" and "YData"  
```{r}
n = 100
p = 500
sigma_noise = 0.5
beta = rep(0, p)
beta[1:6] = c(5,10,3,80,90,10)
XData = matrix(rnorm(n*p,sd=10), nrow = n, ncol=p)
X=XData
for (i in 1:500){
  X[,i]=((X[,i]-sum(X[,i])/n))/((var(X[,i])*99/100)^0.5)
}
YData = X %*% beta + rnorm(n, sd = sigma_noise)
YData=YData-sum(YData)/100
XData=X
```


# Algorithm for LASSO

## Coordinate Descent for LASSO(lambda=1)
```{r}
library(zhouyahomework1)
# Coordinate Descent for LASSO
betaHat1list = CoordinateDescent(XData,YData,1)
betaHat1=unlist(betaHat1list["betahat"])
diff1 = betaHat1 - beta
# L2 loss
L2Loss1 = sqrt(sum(diff1^2))
# True Positive Rate
TP1 = sum(abs(beta)>0 & abs(betaHat1)>0) / sum(abs(beta)>0)
# True Negative Rate
TN1 = sum(abs(beta)==0 & abs(betaHat1)==0) / sum(abs(beta)==0)
# Numbers of Iteration
ite1=unlist(betaHat1list["iteration"])
# Values of Objective Function
f1=unlist(betaHat1list["object function"])
```


## Proximal Operator for LASSO(lambda=1)
```{r}
library(zhouyahomework1)
# Proximal Operator for LASSO
betaHat2list=ProximalOperator(XData, YData, 1)
betaHat2 = unlist(betaHat2list["betahat"])
diff2 = betaHat2 - beta
# L2 loss
L2Loss2 = sqrt(sum(diff2^2))
# True Positive Rate
TP2 = sum(abs(beta)>0 & abs(betaHat2)>0) / sum(abs(beta)>0)
# True Negative Rate
TN2 = sum(abs(beta)==0 & abs(betaHat2)==0) / sum(abs(beta)==0)
# Numbers of Iteration
ite2=unlist(betaHat2list["iteration"])
# Values of Objective Function
f2=unlist(betaHat2list["object function"])
```


## Compare these two algorithms
- Some Indexes
- L2 loss and True Positive rate
```{r}
cat("the L2 loss for Coordinate Descentand Proximal Operator 
    are:",L2Loss1,L2Loss2)
cat("the True Positive Rate for Coordinate Descent and Proximal 
    Operator are:",TP1,TP2)
```

## Compare these two algorithms
- True Negative Rate and numbers of iteration
```{r}
cat("the True Negative Rate for Coordinate Descent and Proximal 
    Operator are:",TN1,TN2)
cat("the numbers of iteration for Coordinate Descent and Proximal 
    Operator are:",ite1,ite2)
```

## Compare these two algorithms
- The System time for lambda=1
```{r}
system.time(CoordinateDescent(XData,YData,1))
system.time(ProximalOperator(XData, YData, 1))
```

## Compare these two algorithms
- The following plot for values of objective funcion and corressponding objective funcions
- The "X-axis" represents iterations and the "Y-axis" represents values of objective function
- The red line is for Proximal Operator while the black is for Coordinate Descent
```{r}
# Values of Objective Funcion
f11=f1[1:ite1]
f22=f2[1:ite2]
```

## Compare these two algorithms
```{r}
plot(1:ite2,f22,xlab="iteration",ylab="object function",type="s",col=2)
lines(1:ite1,f11,col=1)
```

# Conclusion
## Conclusion for lambda=1
- Coordinate Descent has less L2 loss but both will
- Both will in TP and TN
- Coordinate Descent has far less iteration numbers
- Coordinate Descent has far less system.time

<div class="red2">
Coordinate Descent for LASSO is better if lambda=1!
</div>


# Thank You!
# Written by Zhou Ya and guided by He shiyuan
# get more information <yazhou@ruc.edu.cn>
